Inferring the rate of Earth-like exoplanets from noisy data

### 2014-03-24 document/ms.tex
adding Gaussian process smoothness prior on bin heights

% Document specific variables.
\newcommand{\rate}{\ensuremath{\eta}}
\newcommand{\ratepars}{\ensuremath{\theta}}
\newcommand{\obs}[1]{\ensuremath{\hat{#1}}}
\newcommand{\radius}{\ensuremath{r}}
\newcommand{\period}{\ensuremath{T}}
\newcommand{\completeness}{\ensuremath{P_\mathrm{c}}}
\newcommand{\transitprob}{\ensuremath{P_\mathrm{t}}}

@@

Now we will make the further assumption that every candidate in our sample of
detected exoplanets is an independent Poisson sample from the population
described by our rate function.
Under this assumption, the likelihood of the catalog conditioned on a set of
parameters \ratepars\ is
\begin{eqnarray}
\ln p(\period,\,\radius\,|\,\ratepars) &\propto&
\sum_{k=1}^K \ln\obs{\rate} (\period_k,\,\radius_k;\,\ratepars)
- \int \obs{\rate} (\period,\,\radius;\,\ratepars) \dd\period\dd\radius
\quad.
\end{eqnarray}

\hoggtodo{How is this related to the version of the likelihood that doesn't
include the normalization. What is the best way to introduce both forms?}

>>>>

% Document specific variables.
\newcommand{\rate}{\ensuremath{\eta}}
\newcommand{\ratepars}{\ensuremath{\theta}}
\newcommand{\obs}[1]{\ensuremath{\hat{#1}}}
\newcommand{\radius}{\ensuremath{R}}
\newcommand{\period}{\ensuremath{T}}
\newcommand{\completeness}{\ensuremath{P_\mathrm{c}}}
\newcommand{\transitprob}{\ensuremath{P_\mathrm{t}}}

@@

Now we will make the further assumption that every candidate in our sample of
detected exoplanets is an independent Poisson sample from the population
described by our rate function.
Under this assumption, the likelihood of the catalog conditioned on a set of
parameters \ratepars\ is (see Appendix XXXXX for a derivation)
\begin{eqnarray}
\ln p(\period,\,\radius\,|\,\ratepars) &\propto&
\sum_{k=1}^K \ln\obs{\rate} (\period_k,\,\radius_k;\,\ratepars)
- \int \obs{\rate} (\period,\,\radius;\,\ratepars) \dd\period\dd\radius
\quad.
\end{eqnarray}
